My title

### 2024-03-28 paper/paper.qmd
Update readme on how to obtain data, and update the table on the paper

| Variable | New Name   | Description                     | Example |
|----------|------------|---------------------------------|---------|
| sex      | sex        | Respondent's gender             |2(FEMALE)|
| HEALTH   | health     | The year of the survey recorded | 2007    |
| SATHEALT | AGE        | The age of the respondents      | 23      |
| PHYSHLTH | Phys_Health| Respondents' physical health    | MALE    |

>>>>

| Variable | New Name  | Description                   | Example |
|----------|-----------|-------------------------------|---------|
| sex      | sex       | Respondent's gender           | Female  |
| age      | age       | Respondent's age              | 25      |
| HEALTH   | health    | Respondents' health condition | Good    |
| PHYSHLTH | phys_days | Days of Respondents' physical health being not good   | 15      |
| MNTLHLTH | ment_days | Days of Respondents' mental health being not good     | 20      |
| DEPRESS  | depress   | Whether respondents have been told having depression  | Yes     |
